### 2022-08-02 paper/akweury/document.tex
update eval

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.20 & 8.90 & 8.80\\ 
		\hline
		Median					& 4.87 & 5.82 & 5.66 \\ 
		\hline
		$ 5^\circ $ 			& 0.51 & 0.43 & 0.44 \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.78 \\
		\hline
		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
		\hline
		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}

>>>>

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
	\caption{SVD}
\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
		\caption{Trip-Net}
	\end{subfigure}

		\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_img.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.20 & 8.90 & 8.30\\ 
		\hline
		Median					& 4.87 & 5.82 & 5.14 \\ 
		\hline
		$ 5^\circ $ 			& 0.51 & 0.43 & 0.49 \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.80 \\
		\hline
		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
		\hline
		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}
